An Hypernetwork Approach to Accurately Measure Technological Innovation \bigskip\\ \textit{Methods and Results}

### 2016-01-25 Docs/Proposal/patents.tex

\begin{abstract}
Patents are a central proxy in the study of the economy of innovation. Indeed, the information contained in relations between patents reflects the underlying structure of the socio-technological system of research and development in innovative companies. Whereas recent focus was mainly on the study of patterns in the inter-patent citation network, taking technological fields as externally fixed, we propose a novel approach based on semantic analysis of patents textual contents. Indeed, measures such as co-occurences and repetitions of keywords should contain a slightly different information than the one extracted from the citation network, as for example links between domains, or informal domains that could appear as communities in the semantic network. The aim of this project is to investigate the nature and extent of this information, by the mining of regular patterns in features that should be established. We expect to test various features crossing measures extracted from both dynamic citation and semantic network, by unsupervised, and supervised if needed, datamining techniques. Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and be able to systematically differentiate innovatives from imitating patents.
\end{abstract}

@@

The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including datamining and network analysis~\cite{newman2010networks} has shed a new light on the approach. With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation. As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g. in the recent analysis on 20th century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation should show special patterns which understanding must have positive feedback on the economy.
% TODO Est-ce qu'il y a déjà un papier d'Aghion qui fait le lien entre croissance et connaissance de l'innovation ? Genre Aghion, P., & Howitt, P. (2005). Growth with quality-improving innovations: an integrated framework. Handbook of economic growth, 1, 67-110. ?
% si oui est-ce que c'est intéressant de le citer à cet endroit ?
This project aims thus to fullfill the objective of exploring the potentialities of a precise measure of innovation through the mining of different aspects of patents data.

@@

\begin{itemize}
\item Project definition, litterature review - AB, JR, PA - ETA 10h
\item Thematic framing (possible features, precise objectives) - AB, JR - ETA 4h
\item Technical aspects (database management, text-mining implementation : JR ; citation network, technological class network : AB) - AB, JR - ETA 20h
\item Empirical datamining - AB, JR - ETA 25h
\item Theoretical feedback, revision of mining techniques - AB, JR, PA - ETA 10h
\item Theoretical modeling, results interpretation, perspectives - AB, PA - ETA ?
\end{itemize}

>>>>

\begin{abstract}
Patents are a central proxy in the study of the economy of innovation. Indeed, the information contained in relations between patents reflects the underlying structure of the socio-technological system of research and development in innovative companies. Whereas recent focus was mainly on the study of patterns in the inter-patent citation network, taking technological fields as externally fixed, we propose a novel approach based on semantic analysis of patents textual contents. Indeed, measures such as co-occurences and repetitions of keywords should contain a slightly different information than the one extracted from the citation network, as for example links between domains, or informal domains that could appear as communities in the semantic network. The aim of this project is to investigate the nature and extent of this information, by the mining of regular patterns in features that should be established. We expect to test various features crossing measures extracted from both dynamic citation and semantic network, by unsupervised, and supervised if needed, data-mining techniques. Expected results are to unveil the potentialities of such approach, and in the case of significant information, to apply it to classify patents and be able to systematically differentiate innovative from imitating patents.
\end{abstract}

@@

The study of innovation through the lens of technological patents is not a novel idea~\cite{basberg1987patents} but the recent rise of new methods and computational abilities, including data-mining and network analysis~\cite{newman2010networks} has shed a new light on the approach. With methods relatively close to applied epistemology studies such as citation dynamics modeling~\cite{2013arXiv1310.8220N} or co-autorships networks analysis~\cite{2014arXiv1402.7268S}, recent works have studied patents citation network to understand the processes of technological innovation. As in science, where reflexivity is crucial and is becoming a mandatory step to build future research agendas, as e.g. in the recent analysis on 20th century physics~\cite{Sinatra:2015yu}, the structure of technology and particularly of technological innovation should show special patterns which understanding must have positive feedback on the economy.
% TODO Est-ce qu'il y a déjà un papier d'Aghion qui fait le lien entre croissance et connaissance de l'innovation ? Genre Aghion, P., & Howitt, P. (2005). Growth with quality-improving innovations: an integrated framework. Handbook of economic growth, 1, 67-110. ?
% si oui est-ce que c'est intéressant de le citer à cet endroit ?
This project aims thus to fullfill the objective of exploring the potentialities of a precise measure of innovation through the mining of different aspects of patents data.

@@

\begin{itemize}
\item Project definition, literature review - AB, JR, PA - ETA 10h
\item Thematic framing (possible features, precise objectives) - AB, JR - ETA 4h
\item Technical aspects (database management, text-mining implementation : JR ; citation network, technological class network : AB) - AB, JR - ETA 20h
\item Empirical datamining - AB, JR - ETA 25h
\item Theoretical feedback, revision of mining techniques - AB, JR, PA - ETA 10h
\item Theoretical modeling, results interpretation, perspectives - AB, PA - ETA ?
\end{itemize}

### 2016-01-25 Docs/WorkingPapers/methods.tex

Text processing operations are implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{} % cite nltk
which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations. Source code is openly available on the repository of the project\footnote{at \texttt{url}}.
% TODO je suis pour ouvrir le repo une fois qu'on aura la majorité du taf faite, je sais pas ce que t'en penses ? c'est une nécessité pour ouverture et reproducibilité ; sans ça aucune valeur à ce qu'on prétend dans le papelard.
Steps one to three are directly done using built-in functions of the library. Step four needs a particular treatment that we propose as an extension of the original method for large corpuses, which is detailed in the following.

\paragraph{Bootstrap on random subcorpuses for relevance estimation}

Once multi-stems have been extracted, one scores them by \emph{unithood}, defined for the multi-stem $i$ by $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the number of apparitions of the multi-stem over the whole corpus and $l_i$ its length in words. Let $K_w$ the maximal number of relevant keywords per patent. If $N$ is the total number of relevant keywords extracted 
The heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $4\cdot N$ keywords on the whole corpus, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of the stem, compared to an uniform distribution within the whole corpus. More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the termhood score as
\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}
\]

@@

>>>>

Text processing operations are implemented in \texttt{python} in order to use the \texttt{nltk} library~\cite{bird2006nltk} which is highly ergonomic and supports most advanced state-of-the-art natural language processing operations. Source code is openly available on the repository of the project\footnote{at \texttt{url}}.
% TODO je suis pour ouvrir le repo une fois qu'on aura la majorité du taf faite, je sais pas ce que t'en penses ? c'est une nécessité pour ouverture et reproducibilité ; sans ça aucune valeur à ce qu'on prétend dans le papelard.
Steps one to three are directly done using built-in functions of the library. Step four needs a particular treatment that we propose as an extension of the original method for large corpuses, which is detailed in the following.

\paragraph{Bootstrap on random sub-corpuses for relevance estimation}

Once multi-stems have been extracted, one scores them by \emph{unithood}, defined for the multi-stem $i$ by $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the number of apparitions of the multi-stem over the whole corpus and $l_i$ its length in words. Let $K_w$ the maximal number of relevant keywords per patent. If $N$ is the total number of relevant keywords extracted, that we consider as a parameter, the heuristic described in~\cite{chavalarias2013phylomemetic} proposes a first filtration of $4\cdot N$ keywords on the whole corpus, and then a filtration on a secondary score called \emph{termhood}, computed as a chi-squared score on the distribution of the stem, compared to an uniform distribution within the whole corpus. More precisely, one computes the co-occurence matrix $(M_{ij})$, defined as the number of patents where stems $i$ and $j$ appear together, what allows to define the \emph{termhood} score as
\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}
\]

Let $X = \{x_1,\ldots ,x_N\}$ a discrete set and $X_1,\ldots ,X_K \in \mathcal{P}(X)$. We write $X_k = \{x_1^{(k)},\ldots ,x_{N_k}^{(k)}\}$. Exact probability distributions within sets are determined directly in $O(\sum_{k=1}^{K}{N_k})$.

@@

\textit{From proposal : }

\begin{itemize}
\item Citation relative centrality regarding technological or semantic classes : given a partition of $\mathcal{P}$ represented by a classification function $C$ (constructed for example by clustering or community detection within technological or semantic networks), a vector feature is for patent $i$
\[
\left(\frac{\sum_{j\in c}Cit^{out}(i,j)}{\sum_{j\in c}Cit^{in}(i,j)}\right)_{c\in C(\mathcal{P})}
\]
\item Dynamic evolution of classification vector : if $C_t$ is stratified over successive time periods indexed by time $t$, either $\Delta \vec{C}_t (i)$ if $\vec{C}_t$ is a vector of probabilities to belong to each class (in case of a Bayesian approach), or $\Delta (C_t(j))_{Cit(i,j,t)\neq 0}$ in case of a deterministic approach, could both be interesting features.
\item Deviation from the expected classes given position in other layers of the hypernetwork (it would need explorations if these conditional probabilities first can be well estimated, then if they contain relevant information).
\end{itemize}
